DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-07-02 ase2017/paper.tex
discussed about safe digital controllers
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

\renewcommand{\baselinestretch}{0.991}
\newcommand\tool{{DSSynth Toolbox}\xspace}
\newcommand{\fwl}[1]{\mathcal{FWL}[#1]}

@@

\begin{abstract}
We present an automated MATLAB Toolbox, named as DSSynth 
(Digital-System Synthesizer), to synthesize sound digital controllers 
for physical plants that are represented as linear time-invariant
systems with single input and output. In particular, DSSynth synthesizes digital 
controllers that are sound w.r.t. the stability specification by taking into account finite word-length 
effects in their representation. DSSynth considers the complete range
of approximations, including time discretization, quantization effects, 
and finite-precision arithmetic (and its rounding errors). 
Currently, there are two DSSynth versions for synthesizing digital controllers for physical plants 
represented by transfer function or state-space equations: a command-line and 
a MATLAB application. The resulting toolbox 
enables application of program synthesis to real-world control engineering systems.
\end{abstract}

@@

Control theory targets the construction of reliable systems by providing mathematical guarantees about the stability and the desired 
performance of closed-loop dynamics, where outputs of discrete plant $G(z)$ 
are fed back and compared to a reference signal to which a (designed) 
controller $C(z)$ should steer~\cite{astrom1997computer}. 
Fig.~\ref{fig:typical-control-system} shows a typical closed-loop digital control system.
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
\caption{Typical Closed-loop Control System.}
\label{fig:typical-control-system}
\end{figure}

@@

Recently, a new methodology to synthesize digital control systems has been proposed, 
named DSSynth (Digital-System Synthesizer)~\cite{abate2017, abatecav2017}, 
which is based on the Counter-Example Guided Inductive Synthesis 
(CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. Here, CEGIS is used
as a program synthesis engine that is able to generate sound digital controllers for highly non-trivial 
control system specifications with a very high degree of automation. The program synthesis engine 
uses a specification as starting point, and subsequently produces a sequence of candidate 
programs from a given template. The candidate programs are iteratively refined to eventually 
satisfy the specification. Modern synthesis engines such as the one used here combine automated testing, genetic algorithms 
and SMT-based automated reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
Using the CEGIS-based approach, DSSynth synthesizes stable digital controllers
for a given physical plant represented by either transfer functions or state-space equations~\cite{abate2017,abatecav2017}.

@@

We use two different instantiations of the synthesiser
in order to find stable and safe digital
controllers. The two approaches differ in
the manner in which they check the safety specification
for all reachable states.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
{\scriptsize
\centering
\resizebox{.43\textwidth}{!}
{
  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=.6cm, column sep=.9cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \coordinate (aux3);
   \& \coordinate (aux4);
   \&;\\
   \coordinate (aux5);
   \& \coordinate (aux6);
   \&;\\
   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=6cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc ~~~~~~~~~~~~Verify},] (verif) {};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc 1.Safety}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 2.Precision}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=2cm]verif.center) {{\sc 3.Complete}};
     %\node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc 5.Sampling}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \& \\
   \node[minimum height=0cm] (gp) {\sf Program Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based \\ \sf Verifier};
   \node (fp)  at ([xshift=0cm]aux.center) {\sf Fixed-point \\ \sf Arithmetic\\ \sf Verifier};
   \node (sv)  at ([xshift=2cm]aux.center) {\sf Completeness\\ \sf Verifier};
   %\node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
   }   
    \\
  };

@@

The first approach, presented in Fig.~\ref{fig:CEGIS-precision-increment}, 
uses a multi-staged verification process. 
It starts by devising a digital controller that stabilizes the model while remaining safe for a
pre-selected time horizon ($k$) and a single initial state; then, it
employs a multi-staged verification process as follows:
(i) The first verification stage ({\sc safety}) checks that the candidate
solution, which we synthesized to be safe for at least one initial
state, is safe for \emph{all} possible initial states, i.e., does not reach
an unsafe state within $k$ steps.
(ii) The second verification stage ({\sc precision})
 restores soundness with respect to the plant precision
by using interval arithmetic \cite{moore1966interval} to validate the 
operations performed by the previous stage. 
(iii) The third verification stage ({\sc complete}) checks that the current
$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
completeness threshold $\overline{k}$ for the current candidate controller 
$K$~\cite{abatecav2017}, i.e., the number of
iterations required to sufficiently unwind the closed-loop state-space
model such that the boundaries are not violated for any larger number of
iterations, and
check that $k{\geq}\overline{k}$.

\begin{figure}
\centering
{\scriptsize
  \resizebox{.5\textwidth}{!}
  {
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \&\node[fill=gray!20,align=center,xshift=-1.5cm] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
   \& \coordinate (aux); \\ 
   \&
   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
      \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc PASS};
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \&
   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
    }\\
  };
  \path
    (pre.east) edge node[align=center] {} (abstract.west)
    (abstract.south) edge node{} (synth.north)
    ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
    (aux) edge (abstract.east) 
    (verify.east) edge (done.west);
  \path
    ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {} ([xshift=0.6cm]synth.south) 
    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {} ([xshift=-.6cm]KSAT.north)
    ([yshift=.5cm]AAV.east) edge node{} ([yshift=.5cm]AAC.west)
    ([yshift=-.5cm]AAC.west) edge node{} ([yshift=-.5cm]AAV.east)
    (AAC.north) edge node{} ([xshift=4.9cm]verify.south)
    ([xshift=-5cm]verify.south) edge node{} (AAV.north);
  \path[-] 
     (verify.north) edge node {C-ex} (aux);
\end{tikzpicture}
}
}
\caption{Abstraction-based CEGIS}
\label{fig:CEGARIS} 
\end{figure}

@@

\noindent where \texttt{plant} is the physical plant in state-space or transfer function representation, 
\texttt{intBits} is the integer part, \texttt{fracBits} is the fractional part, \texttt{maxR} and \texttt{minR} 
are the maximum and minimum dynamic range, respectively (cf. steps $2$ and $3$ of Fig.~\ref{fig:synthesis-flow}).
%
After executing the \texttt{synthesize} command in MATLAB, 
\tool provides the synthesized digital controller, according to the digital system representation.

@@

Our experimental evaluation consists of $18$ SISO control system benchmarks 
extracted from the literature~\cite{abate2017,abatecav2017,bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16},
which include physical plants for unmanned aerial vehicle (UAV), cruise control system, 
spring-mass damper, satellite, direct current (DC) servo motor, helicopter, 
inverted pendulum, pendulum, magnetic suspension, magnitezed pointer, 1/4 car suspension, 
computer tape driver, flexible beam, guidance system, USCG cutter tampa, continuous stirred tank reactor, 
voltage regulator, and an acrobot control system.

@@

The main objectives of our experimental evaluation is to (1) evaluate the \tool performance 
to produce stable controllers, and also (2) confirm the stability of the synthesized digital 
controllers outside of our model, using both the transfer function and state-space representations.

@@

\textcolor{red}{Why are the experiments only mentioning stable controllers? Up until this point, we discuss stable and safe controllers.}

For our experiments, we observed that the \tool correctly synthesizes stable digital controllers 
for our set of benchmarks represented by transfer functions or state-space equations. 
We employed a diverse set of real-world benchmarks extracted from the control literature. 
However, note that this set of benchmarks is still limited within the scope of this paper, and 
the performance may not be generalized to other benchmarks. 
The median runtime for our benchmarks set is $124$\,s, and the average synthesis time amounts 
to $35.5$\,s for closed-loop control systems represented by state-space equations, while 
for transfer functions, the average synthesis time amounts to $123.6$\,s.

Additionally, we are able to reproduce the stability for all evaluated control system benchmarks.
As an example, we have reproduced the stability property in the synthesized controller 
for a DC motor plant described in Eq.~\eqref{tf-synth-controller}, simulating the step response 
in MATLAB. Fig.~\ref{tf-step-response} shows that the digital controller 
synthesized by the \tool stabilizes the closed-loop control system using 
the series connection (as shown in Fig.~\ref{fig:typical-control-system}) for the DC motor plant. 
We have applied this procedure to all synthesized controllers to confirm the reliability of our experimental results.
%
\begin{equation}
\label{tf-synth-controller}
C(z)=\frac{-0.3466796875z+0.015625}{-0.5z^{2}+0.19921875z}.
\end{equation}

@@

The digital controllers synthesized by \tool are all stable using the MATLAB step response
as a validation procedure, which means that our results are reliable for control engineers. 
A link to the full experimental environment, including the scripts to reproduce the results, 
all benchmarks, videos, documentation and the tool, is provided online.\footnote{\url{www.dsverifier.org}}

>>>>

\renewcommand{\baselinestretch}{0.99}
\newcommand\tool{{DSSynth Toolbox}\xspace}
\newcommand{\fwl}[1]{\mathcal{FWL}[#1]}

@@

\begin{abstract}
We present an automated MATLAB Toolbox, named as DSSynth 
(Digital-System Synthesizer), to synthesize sound digital controllers 
for physical plants that are represented as linear time-invariant
systems with single input and output. In particular, DSSynth synthesizes digital 
controllers that are sound w.r.t. the stability and safety specifications by taking into account finite word-length 
effects in their representation. DSSynth considers the complete range
of approximations, including time discretization, quantization effects, 
and finite-precision arithmetic (and its rounding errors). 
Currently, there are two DSSynth versions for synthesizing digital controllers for physical plants 
represented by transfer function or state-space equations: a command-line and 
a MATLAB application. The resulting toolbox 
enables application of program synthesis to real-world control engineering systems.
\end{abstract}

@@

Control theory targets the construction of reliable systems by providing mathematical guarantees about the stability and the desired 
performance of closed-loop dynamics, where outputs of discrete plant $G(z)$ 
are fed back and compared to a reference signal to which a 
controller $C(z)$ should steer~\cite{astrom1997computer}. 
Fig.~\ref{fig:typical-control-system} shows a typical closed-loop digital control system.
%
\begin{figure}[ht!]
\centering
\includegraphics[width=0.4\textwidth]{closedloopseries.pdf}
\caption{Typical Closed-loop Control System.}
\label{fig:typical-control-system}
\end{figure}

@@

Recently, a new methodology to synthesize digital control systems has been proposed, 
named DSSynth (Digital-System Synthesizer)~\cite{abate2017, abatecav2017}, 
which is based on the Counter-Example Guided Inductive Synthesis 
(CEGIS) approach~\cite{DBLP:conf/asplos/Solar-LezamaTBSS06}. CEGIS is used
as a program synthesis engine that is able to generate sound digital controllers for highly non-trivial 
control system specifications with a very high degree of automation. The program synthesis engine 
uses a specification as starting point, and subsequently produces a sequence of candidate 
programs from a given template. The candidate programs are iteratively refined to eventually 
satisfy the specification. Modern synthesis engines such as the one used here combine automated testing, genetic algorithms 
and SMT-based reasoning~\cite{DBLP:journals/corr/AlurFSS16a, DBLP:conf/lpar/DavidKL15}. 
Using the CEGIS-based approach, DSSynth synthesizes stable digital controllers
for a given physical plant represented by either transfer functions or state-space equations~\cite{abate2017,abatecav2017}.

@@

We use two different instantiations of the synthesiser
in order to find stable and safe digital
controllers. The two approaches differ in
the manner in which they check the safety specification
for all reachable states.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{figure}[htb]
{\scriptsize
\centering
\resizebox{.43\textwidth}{!}
{
  \begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, initial text=, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center
},
          row sep=.6cm, column sep=.9cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \&;\\
   \coordinate (aux3);
   \& \coordinate (aux4);
   \&;\\
   \coordinate (aux5);
   \& \coordinate (aux6);
   \&;\\
   \node[minimum width=1.5cm, minimum height=0.6cm, fill=gray!20] (synth) {{\sc Synthesize}};
   \&
   complexnode/.pic={ 
     \node[rectangle,draw,dotted,
	minimum width=6cm,
	minimum height=1cm,
        pattern=north west lines, pattern color=gray!20,
	label={\sc ~~~~~~~~~~~~Verify},] (verif) {};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif1) at ([xshift=-2cm]verif.center) {{\sc 1.Safety}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif2) at ([xshift=0cm]verif.center) {{\sc 2.Precision}};
     \node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif3) at ([xshift=2cm]verif.center) {{\sc 3.Complete}};
     %\node[minimum width=1cm, minimum height=0.6cm, fill=gray!20] (verif4) at ([xshift=3.1cm]verif.center) {{\sc 5.Sampling}};
   } 
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \& \\
   \node[minimum height=0cm] (gp) {\sf Program Search};
   \&
   complexnode/.pic={ 
     \coordinate (aux);
   \node (bmc) at ([xshift=-2cm]aux.center) {\sf BMC-based \\ \sf Verifier};
   \node (fp)  at ([xshift=0cm]aux.center) {\sf Fixed-point \\ \sf Arithmetic\\ \sf Verifier};
   \node (sv)  at ([xshift=2cm]aux.center) {\sf Completeness\\ \sf Verifier};
   %\node (cv)  at ([xshift=3.1cm]aux.center) {\sf Sampling\\Verifier};
   }   
    \\
  };

@@

The first approach, presented in Fig.~\ref{fig:CEGIS-precision-increment}, 
uses a multi-staged verification process. 
It starts by devising a digital controller that stabilizes the model while remaining safe for a
pre-selected time horizon ($k$) and a single initial state; then, it
employs a multi-staged verification process as follows:
(i) The first verification stage ({\sc safety}) checks that the candidate
solution, which we synthesized to be safe for at least one initial
state, is safe for \emph{all} possible initial states, i.e., does not reach
an unsafe state within $k$ steps.
(ii) The second verification stage ({\sc precision})
 restores soundness with respect to the plant precision
by using interval arithmetic \cite{moore1966interval} to validate the 
operations performed by the previous stage. 
(iii) The third verification stage ({\sc complete}) checks that the current
$k$ is large enough to ensure safety for any $k'{>}k$.  Here, we compute the
completeness threshold $\overline{k}$ for the current candidate controller 
$K$~\cite{abatecav2017}, i.e., the number of
iterations required to sufficiently unwind the closed-loop state-space
model such that the boundaries are not violated for any larger number of
iterations, and
check that $k{\geq}\overline{k}$.
%
\begin{figure}
\centering
{\scriptsize
  \resizebox{.5\textwidth}{!}
  {
\begin{tikzpicture}[scale=0.3,->,>=stealth',shorten >=.2pt,auto, semithick, ampersand replacement=\&,]
  \matrix[nodes={draw, fill=none, shape=rectangle, minimum height=.2cm, minimum width=.2cm, align=center},row sep=.8cm, column sep=.2cm] {
   \coordinate (aux1);
   \& \coordinate (aux2);
   \& ;\\
   \&\node[fill=gray!20,align=center,xshift=-1.5cm] (pre) {{\sc 1. pre-}\\{\sc processing}};
   \& \node[fill=gray!20,align=center] (abstract) {\sc 4. abstract};
   \& \coordinate (aux); \\ 
   \&
   \& \node[fill=gray!20,align=center] (synth) {\sc 2. synthesize};
   \& \node[fill=gray!20,align=center, minimum width=4cm] (verify) {\sc 3. verify ($\phi$)};
      \node[draw=none] (SAT) at ([xshift=2.7cm,yshift=-.3cm]verify)  {\sc PASS};
   \& \node[ellipse, fill=gray!20] (done) {{\sc Done}};\\
   \&
   \& \node[draw,rectangle,align=center] (KSAT) {Program \\ Search};
   \& complexnode/.pic={
     \coordinate (AA);
     \node[draw,rectangle,align=center] (AAV) at ([xshift=-1.5cm]AA.center) {Abstract\\Acceleration};
     \node[draw,rectangle,align=center] (AAC) at ([xshift=1.5cm]AA.center) {Abstraction \\ Verifier};
    }\\
  };
  \path
    (pre.east) edge node[align=center] {} (abstract.west)
    (abstract.south) edge node{} (synth.north)
    ([yshift=1em]synth.east) edge node {$K$} ([yshift=1em]verify.west)
    (aux) edge (abstract.east) 
    (verify.east) edge (done.west);
  \path
    ([xshift=+.6cm]KSAT.north) edge[left] node[xshift=-.3cm] {} ([xshift=0.6cm]synth.south) 
    ([xshift=-.6cm]synth.south) edge node[align=center,xshift=.3cm] {} ([xshift=-.6cm]KSAT.north)
    ([yshift=.5cm]AAV.east) edge node{} ([yshift=.5cm]AAC.west)
    ([yshift=-.5cm]AAC.west) edge node{} ([yshift=-.5cm]AAV.east)
    (AAC.north) edge node{} ([xshift=4.9cm]verify.south)
    ([xshift=-5cm]verify.south) edge node{} (AAV.north);
  \path[-] 
     (verify.north) edge node {C-ex} (aux);
\end{tikzpicture}
}
}
\caption{Abstraction-based CEGIS}
\label{fig:CEGARIS} 
\end{figure}

@@

\noindent where \texttt{plant} is the physical plant in state-space or transfer function representation, 
\texttt{intBits} is the integer part, \texttt{fracBits} is the fractional part, \texttt{maxR} and \texttt{minR} 
are the maximum and minimum dynamic range, respectively (cf. steps $2$ and $3$ of Fig.~\ref{fig:synthesis-flow}).
%
After executing the \texttt{synthesize} command, 
\tool provides the synthesized digital controller, according to the implementation aspects.

@@

Our evaluation consists of $18$ SISO control system benchmarks 
extracted from the literature~\cite{abate2017,abatecav2017,bouabdallah, acrobot,cstr,KOKOTOVIC198023,gajic2008optimal,Franklin15, maglev, converters, CTMS,DBLP:journals/tc/BessaIPCF17,DBLP:journals/dafes/BessaICF16},
which include physical plants for unmanned aerial vehicle (UAV), cruise control system, 
spring-mass damper, satellite, direct current (DC) servo motor, helicopter, 
inverted pendulum, pendulum, magnetic suspension, magnitezed pointer, 1/4 car suspension, 
computer tape driver, flexible beam, guidance system, USCG cutter tampa, continuous stirred tank reactor, 
voltage regulator, and an acrobot control system.

@@

The main objectives of our experimental evaluation is to (1) evaluate the \tool performance 
to produce stable and safe controllers, and also (2) confirm the stability and safety of the synthesized digital 
controllers outside of our model using MATLAB. %, using both the transfer function and state-space representations.

@@

%\textcolor{red}{Why are the experiments only mentioning stable controllers? Up until this point, we discuss stable and safe controllers.}

For our experiments, we observed that the \tool correctly synthesizes stable and safe digital controllers 
for our set of benchmarks represented by transfer functions or state-space equations. 
We employed a diverse set of real-world benchmarks extracted from the control literature. 
However, note that this set of benchmarks is still limited within the scope of this paper, and 
the performance may not be generalized to other benchmarks. 
The median runtime for our benchmarks set is $124$\,s, and the average synthesis time amounts 
to $35.5$\,s for closed-loop control systems represented by state-space equations, while 
for transfer functions, the average synthesis time amounts to $123.6$\,s.

Additionally, we are able to reproduce the stability and safety for all evaluated control system benchmarks.
As an example, we have reproduced the stability property in the synthesized controller 
for a DC motor plant described in Eq.~\eqref{tf-synth-controller}, simulating the step response 
in MATLAB. Fig.~\ref{tf-step-response} shows that the digital controller 
synthesized by the \tool stabilizes the closed-loop control system using 
the series connection (as shown in Fig.~\ref{fig:typical-control-system}) for the DC motor plant. 
We have applied this procedure to all synthesized controllers to confirm the reliability of our experimental results.
%
\begin{equation}
\label{tf-synth-controller}
C(z)=\frac{-0.3466796875z+0.015625}{-0.5z^{2}+0.19921875z}.
\end{equation}

@@

%The digital controllers synthesized by \tool are all stable using the MATLAB step response
%as a validation procedure, which means that our results are reliable for control engineers. 
The synthesized controllers are also confirmed to be safe outside of our model
representation using MATLAB, which means that our results are reliable for control engineers. 
In particular, we unfold the system dynamics up to a given depth, 
compute the system's input and output via the feedback matrix, and then check the states' bounds.
 A link to the full experimental environment, including the scripts, benchmarks, 
 videos, documentation and the tool, is provided online.\footnote{\url{www.dsverifier.org}}
